Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2017-05-17 1607 - JMC for g2/Paper/JMC_dis.tex
Revised paper after discussions with Andrea

@@

\date{\bf \today, \currenttime}

\begin{abstract}
We revisit the standard analysis of inclusive Deep Inelastic Scattering (DIS)
off nucleons taking into
account the fact that on-shell quarks cannot be present in the final state,
but they rather decay into hadrons. As a consequence, a spin-flip term
associated with the invariant mass of the produced hadrons is generated
non perturbatively, and couples to the target's transversity distribution
function. In inclusive cross sections, this provides an hitherto neglected and
large contribution to the twist-3 part of the $g_2$ structure function, that
can explain the discrepancy between recent calculations and fits of this
quantity. It also provides an extension of both the Burkardt-Cottingham sum rule, putting constraints on the small-$x$ behavior of the transversity
function and can help constraining the nucleon tensor charge, and of the Efremov-Teryaev-Leader sum rule, suggesting a novel way to mwasure the tensor charge of the proton. 
%Perspectives to measure the new spin-flip term, and applications to
%spin-1 targets will be briefly discussed. 
\end{abstract}

@@

The tensor charge is a fundamental property of the nucleon, that is at
present poorly constrained but of fundamental importance, not the least because its knowledge can be used also to put constraints on the search of physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
The tensor charge has been estimated in lattice QCD (see, \eg,
\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn}), but
only limited information is available from direct measurements. Its experimental extraction requires first of all the measurement of the so-called transversity parton distribution function,
denoted by $h_1^q(x)$ (see Ref.~\cite{Barone:2001sp} for a review on transversity and
Refs.~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa} for the most recent
extractions). Secondly, one needs to perform a flavor decomposition and evaluate its integral, that corresponds to the contribution of flavor $q$ to the tensor charge.

@@

In this paper, we discuss a novel way of accessing the transversity parton distribution function (PDF) and measuring the proton's tensor charge in totally inclusive Deep Inelastic Scattering. 
We revisit the standard analysis of inclusive DIS taking into account the fact
that on-shell quarks cannot be present in the final state, but they rather
decay into hadrons (ideally, forming jets of hadrons). This is sufficient to modify the structure of the DIS
cut-diagram, even if none of the hadrons is detected in the final
state. For a proper description of this effect, we include ``jet
correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant. We observe that the inclusion of jet correlators introduces a new
contribution to the inclusive $g_2$ structure function. This term is
proportional to the transversity distribution function multiplied by a
nonperturbative ``jet mass'' parameter, likely much larger than the mass of light quarks, and has the
interesting features that: (a) it violates the Wandzura--Wilczek relation; (b)
it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution; (c) it also extends the Efremov-Teryaev-Leader sum rule, and provides a novel way to measure the proton's tensor charge.
We provide estimates of this new jet-mass induced contribution based on a recent extraction of transversity, and show that it can indeed be very large.

@@

Motivated by large-$x$ mass corrections to inclusive DIS structure functions,
Accardi and Qiu have introduced in the LO handbag diagram 
a ``jet correlator'' (also called ``jet factor'' by Collins and Rogers in Ref.~\cite{Collins:2007ph})
that accounts for invariant mass production in the current jet, and ensures
that leading twist calculations in collinear factorization are consistent with
the requirement imposed by baryon number conservation that $x_B<1$
\cite{Accardi:2008ne}. The jet correlator is depicted in
Figure~\ref{fig:handbags}(a) and is defined as 
\begin{align} 
\Xi_{ij}(l,n_+) =\int
  \frac{\de^4\eta}{(2\pi)^4}\; e^{i l \cdot \eta}\,
    \langle 0|\, {\cal U}^{n_+}_{(+\infty,\eta)}
\,\psi_i(\eta)
             \bar{\psi}_j(0)\,
{\cal U}^{n_+}_{(0,+\infty)}\,   |0 \rangle \ ,
\label{e:xifull}
\end{align} 
In this definition, $l$ is the quark's four-momentum, $\Psi$ the quark field
operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is
the nonperturbative vacuum state. Furthermore, we explicitly guarantee the
correlator's gauge invariance by introducing two Wilson line operators ${\cal
  U}^{n_+}$ along a light-cone plus direction determined by the vector
$n_+$. This path choice for the Wilson line is required by QCD factorization
theorems, and the vector is determined by the particular hard process to which
the jet correlator contributes. For example, in the case of inclusive DIS
discussed in this paper, this is determined by the four momentum transfer $q$
and the proton's momentum $p$.

The correlator $\Xi$ can be parametrized in terms of jet parton correlation
functions (PCFs), using the vectors $l$ and $n_+$: 
\begin{equation}
\Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
+ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
+ \frac{i \Lambda}{2 l \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ ,
\label{e:jetexpansion}
\end{equation} 
where $\Lambda$ is an arbitrary scale, introduced for power counting purposes.
In this parametrization, no terms proportional to $\gamma_5$ enters because of parity invariance. Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes only at twist-4 order, and will not be considered further in this paper. We focus, instead, on the role of chiral odd terms in the $g_2$ structure function up to twist 3. At this order, 
\begin{equation}
  \Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
    + O(\Lambda^2/Q^2)
\label{e:jetexpansion-tw3}
\end{equation} 
is nothing else than the cut quark propagator; note however, that we consider
here the full QCD vacuum rather than the perturbative one (or, in other words, the interacting rather than the free quark fields).
The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral
representation of the cut quark propagator (see, e.g., Sec.~6.3 of
\cite{D'Hoker:2004aa} and Sec.~2.7.2 of \cite{Romao:2013aa}),
\begin{align} 
  \Xi(l) =  
  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu + J_2 (\mu^2)\,\lslash \big] \,
  \delta(l^2 -\mu_j^2) \ ,
\label{e:jetspectral}
\end{align}
where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it
  i.e.}, of the particles going through the cut in the top blob of
Fig.\ref{fig:handbags}(a), and the $J_i$ are the spectral functions of the
quark propagator, also called ``jet functions'' in
\cite{Accardi:2008ne}. These satisfy
\begin{align}
  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
  \int d\mu^2 J_2(\mu^2) = 1 \ .
\label{eq:jetfnsprops}
\end{align}
From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
\begin{align}
  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
  \label{eq:jet_vs_spectral}
\end{align}

\begin{figure*}[bt]
  \centering
  (a)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram0}
  \hfill
  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2}
  \hfill
  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
  \caption{Diagrams contributing to DIS scattering up to twist-3, including a jet correlator in the top part. Note the gluon attaches to both the nucleon and jet correlators. The Hermitian conjugates of diagrams (b) and (c), i.e., with gluons attaching to the right of the cut, are not shown.
  }
  \label{fig:handbags}
\end{figure*}

When inserting the jet correlator in the handbag diagram for inclusive DIS,
the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$, where $x_B$ is the Bjorken invariant. This
induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the
$F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}: 
\begin{align}
  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(\xi(1+\mu^2/Q^2)) \ ,
\label{eq:F2}
\end{align}
where $F_2^{(0)}$ is the structure function calculated with the handbag
diagram sporting a bare quark propagator instead of the jet correlator, and
$\xi=2x_B/(1+\sqrt{1+4x_B^2M^2/Q^2})$ with $M$ the nucleon's mass is the
Nachtmann scaling variable. (We omitted the dependence of the structure
function on $Q^2$ for clarity of notation). In this paper we limit our
attention to effects of order $O(1/Q)$ and therefore can extend the
integration to $\mu^2=\infty$. As a consequence, the jet function $J_2$ decouples and, thanks to the sum rule \eqref{eq:jetfnsprops}, integrates to 1. One then recovers the conventional result, 
\begin{align}
  F_2(x_B) = \Big[ \int_0^\infty d\mu^2\, J_2(\mu^2) \Big] F_2^{(0)}(x_B) 
     + O(\Lambda^2/Q^2) = F_2^{(0)}(x_B)  + O(\Lambda^2/Q^2) \ .
\end{align}
%The same holds true also for the helicity structure function $g_1$.
%
More in general, the jet correlator decouples from the parton correlator $\Phi$ in any inclusive cross section calculation up to $O(1/Q)$, and the inclusive structure functions only depend on the integrated jet correlator 
\begin{equation} 
  \Xi(l^-) \equiv \int \frac{dl^2}{2l^-} d^2 l_T \, \Xi(l) 
    =  \frac{\Lambda}{2 l^-}\,\xi_1 {\bm 1}
    +  \xi_2 \frac{\nslash_-}{2} 
    + \text{higher\ twists}
    % +\frac{\Lambda^2}{4 (l^-)^2}\,\xi_3 \nslash_+
    % + i \frac{\Lambda}{2 l^-} \xi_4 
    % \frac{ \bigl[\nslash_-, \nslash_+ \bigr]}{2}.
\end{equation} 
where 
\begin{align}
\xi_1 &= \int d\mu^2 \frac{\mu}{\Lambda} J_1(\mu^2) 
       \equiv \frac{\mj}{\Lambda},
&
\xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ .
% \\
% \xi_3 &= 0,
% &
% \xi_4 &= \int d\mu^2 \frac{\mu^2}{\Lambda^2} J_1(\mu^2) = \frac{\mjs}{\Lambda^2}.
\end{align} 
Here, $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
% The $\xi_1$ and $\xi_4$ have an interpretation as average invariant mass (and mass squared) of the current jet, and $l^-=q^- + O(1/Q)$ is imposed by 4-momentum conservation at the hard scattering vertex. The $\xi^4$ term contributes at order $O(1/Q^2)$ and is no further considered in this paper. 
It is important to notice that $\xi_2=1$ exactly due to CPT invariance
(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is
dynamically determined. From the analytic properties of spectral functions we
may expect \cite{Accardi:2008ne} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2
(\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the
mass of the pion, due to color confinement effects. Taking into account that
$J_1 < J_2$, we may therefore expect  
\begin{align}
  \label{eq:mjet}
  \mj = O(100 \text{ MeV}) \ .
\end{align}
Although $\mj$ is in general a nonperturbative quantity, it is interesting to
notice that  
\begin{align}
  \label{eq:xi2_chiral_cond}
  \mj = \frac{\Lambda}{4} \int \Tr \big[ \Xi(l) \bm 1] 
   = \langle 0 | \bar \psi_i(0) \psi_i(0) | 0 \rangle
\end{align}
% \todo{[AA] 2 issues here: (1) possible factors of 4. 
% (2) I am neglecting the sum over quarks; we have to fix that somehow but there is a little tension between the quark level $\xi^a$ and the contribution to structure function which is summed and weighted by the electron charge.} 
On the non-perturbative vacuum, this corresponds the contribution of a quark of flavor $q$ to the chiral condensate, and is calculable in principle in lattice QCD.
Considering the perturbative vacuum and calculating the same to leading order in the strong coupling constant, corresponds, instead, to taking the trace of the cut bare-quark propagator to obtain 
$\mj = \,_{\text{pert}} \langle 0
|  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = \mq$, with $\mq$ the quark mass. One recovers, therefore, the result of the calculation with the conventional handbag diagram. 
However, we are here considering non perturbative effects
on the quark fragmentation and $\mj \gtrsim \mq$. Therefore, differently from $J_2$, the $J_1$ function leaves an imprint on the inclusive DIS cross section even in the asymptotic $Q^2 \to \infty$ regime.

%, an example of which we will discuss in the next section.  
%very importantly, this
%quantity can be computed in lattice QCD. 
%\todo{[AA] Are qe sure that $\mj > \mq$??}
%\todo{[AA] Need to discuss connection to quark condensate and tensor charge.}

@@

Extending the analysis of \cite{Accardi:2008ne} to the calculation of twist-3
structure functions requires not only to consider the $\xi_1$ term in the jet
correlator, but also quark-gluon-quark correlators in both the proton and the
vacuum as depicted in Figs.\ref{fig:handbags}(b) and (c), respectively. 
In the former the $\xi_1$ terms contribute to $O(1/Q^2)$, so that up to $O(1/Q)$
these give the same contribution as in the conventional handbag calculation.

The novel element in our analysis is the jet's quark-gluon-quark correlator
$\Xi_A^{\mu}(l,k)$ in diagram \ref{fig:handbags}(c), 
\begin{equation} 
\begin{split} 
  \left(\Xi_A^{\mu} \right)_{ij} &=
   \frac{1}{2}\, \sum_X \int \frac{\de \eta^+\, \de^2 \bm{\eta}_T}{(2\pi)^{3}}\;
   e^{\ii k \cdot \eta}\,
   \langle 0|\,
   {\cal U}^{n_+}_{(+\infty,\eta)}\,
   g A^{\mu}(\eta)\,
   \,\psi_i(\eta)|X\rangle
   \langle X|
             \bar{\psi}_j(0)\,
   {\cal U}^{n_+}_{(0,+\infty)}
   |0\rangle \bigg|_{\eta^-=0} .
\label{e:xi_A}
\end{split} 
\end{equation}  
This diagram and its Hermitian conjugate are not only important to account for
all contribution of order $O(1/Q)$, but also to restore gauge invariance, which is broken in diagram \ref{fig:handbags}(a) due to the different mass
of the incoming and outgoing quark lines, namely, $\mq \neq \mj$.

Rather than directly using the definition \eqref{e:xi_A}, it is convenient to
calculate the inclusive cross section as an integral of the semi-inclusive
one, utilize the QCD equation of motions, sum over all
hadron flavors, and take advantage of  
\begin{align}
  \label{eq:SIDIS_to_DIS}
  \sum_h \int \frac{d^3p_h}{(2\pi)2E_h} \Delta^h(l,p_h) = \Xi(l) \ , 
\end{align}
where $\Delta^h$ is the quark fragmentation correlator for production of a
hadron of flavor $h$ and momentum $p_h$ \cite{Bacchetta:2006tn}. In terms of
the TMD fragmentation functions we are interested in, this reads 
\begin{align}
  \label{eq:SIDIS_to_DIS_TMDlevel}
  \sum_h \int dz d^2p_{hT} z D_1^h(z,p_{hT}) & = \xi_2 = 1   \\
  \sum_h \int dz d^2p_{hT} E^h(z,p_{hT}) & = \xi_1 = \mj / \Lambda\ ,
\end{align}
where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a
function of the hadron's collinear momentum fraction $z$ and transverse
momentum $p_{hT}$, and $E^h(z,p_{hT})$ is a chiral-odd twist-3 function
defined in \cite{Bacchetta:2006tn}.

>>>>

\newcommand{\id}{{\bm 1}
                 %\mathbb{I}
}

%\renewcommand{\Xi}{\Pi}
%\renewcommand{\xi}{\pi}

@@

\date{\bf Thursday, May 4th, 2017}
%\date{\bf \today, \currenttime}

\begin{abstract}
We revisit the standard analysis of inclusive Deep Inelastic Scattering (DIS)
off nucleons taking into  account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons -  a process that can be described in terms of suitable "jet" correlators. As a consequence, a spin-flip term
associated with the invariant mass of the produced hadrons is generated
non perturbatively, and couples to the target's transversity distribution
function. In inclusive cross sections, this provides an hitherto neglected and
large contribution to the twist-3 part of the $g_2$ structure function, that
can explain the discrepancy between recent calculations and fits of this
quantity.  It also provides an extension of the Burkardt-Cottingham sum rule, putting constraints on the small-x behavior of the transversity function, as well as an extension of the Efremov-Teryaev-Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
%Perspectives to measure the new spin-flip term, and applications to
%spin-1 targets will be briefly discussed. 
\end{abstract}

@@

The tensor charge is a fundamental property of the nucleon, that is at
present poorly constrained but of fundamental importance, not the least because its knowledge can be also used to put constraints on the search of physics beyond the Standard Model~\cite{Cirigliano:2013xha,Bhattacharya:2015esa,Courtoy:2015haa}.
The tensor charge has been estimated in lattice QCD (see, \eg,
\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn}), but
only limited information is available from direct measurements. Its experimental extraction requires first of all the measurement of the so-called transversity parton distribution function,
denoted by $h_1^q(x)$ (see Ref.~\cite{Barone:2001sp} for a review on transversity and
Refs.~\cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa} for the most recent
extractions). Secondly, one needs to perform a flavor decomposition and evaluate its integral, that corresponds to the contribution of flavor $q$ to the tensor charge.

@@

In this paper, we discuss a novel way of accessing the transversity parton distribution function (PDF) and measuring the proton's tensor charge in totally inclusive Deep Inelastic Scattering. 
We revisit the standard analysis of inclusive DIS taking into account the fact
that on-shell quarks cannot be present in the final state, but they rather
decay into hadrons, typically forming mini-jets of hadrons. This is sufficient to modify the structure of the DIS
cut-diagram, even if none of the hadrons is detected in the final
state. For a proper description of this effect, we include ``jet
correlators'' into the analysis, and pay particular attention to ensuring that our results are gauge invariant. We observe that jet correlators introduce a new
contribution to the inclusive $g_2$ structure function. This term is
proportional to the transversity distribution function multiplied by a
nonperturbative ``jet mass'' parameter, much larger than the mass of light quarks, and has the interesting features that:
(a) it violates the Wandzura--Wilczek relation;
(b) it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution;
(c) it also extends the Efremov-Teryaev-Leader sum rule, and provides a novel way to measure the proton's tensor charge.
We provide estimates of this new jet-mass-induced contribution based on a recent extraction of transversity, and show that it can indeed be very large.

@@

Motivated by large-$x$ mass corrections to inclusive DIS structure functions,
Accardi and Qiu \cite{Accardi:2008ne} have introduced in the LO handbag diagram 
a ``jet correlator'' (also called ``jet factor'' by Collins and Rogers in Ref.~\cite{Collins:2007ph})
that accounts for invariant mass production in the current region, and ensures
that leading twist calculations in collinear factorization are consistent with
the requirement imposed by baryon number conservation that $x_B<1$
\cite{Accardi:2008ne}. The jet correlator is depicted in
Figure~\ref{fig:handbags}(a) and is defined as 
\begin{align}
\Xi_{ij}(l,n_+) =\int
  \frac{\de^4\eta}{(2\pi)^4}\; e^{i l \cdot \eta}\,
    \langle 0|\, {\cal U}^{n_+}_{(+\infty,\eta)}
\,\psi_i(\eta)
             \bar{\psi}_j(0)\,
{\cal U}^{n_+}_{(0,+\infty)}\,   |0 \rangle \ ,
\label{e:xifull}
\end{align} 
In this definition, $l$ is the quark's four-momentum, $\Psi$ the quark field
operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is
the nonperturbative vacuum state. Furthermore, we explicitly guarantee the
correlator's gauge invariance by introducing two Wilson line operators ${\cal
  U}^{n_+}$ running to infinity first along along a light-cone plus direction determined by the vector $n_+$, then along the direction transverse to that vector, see \cite{Bacchetta:2006tn} for details/ This path choice for the Wilson line is required by QCD factorization theorems, and the vector is determined by the particular hard process to which the jet correlator contributes. For example, in the case of inclusive DIS
discussed in this paper, this is determined by the four momentum transfer $q$
and the proton's momentum $p$.

The correlator $\Xi$ can be parametrized in terms of jet parton correlation
functions (PCFs), using the vectors $l$ and $n_+$: 
\begin{equation}
\Xi(l,n_+) = \Lambda A_1(l^2)\,\id + A_2(l^2)\,\lslash 
+ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
+ \frac{i \Lambda}{2 l \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ ,
\label{e:jetexpansion}
\end{equation} 
where $\Lambda$ is an arbitrary scale, introduced for power counting purposes.
In this parametrization, no terms proportional to $\gamma_5$ enter because of parity invariance. Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes only at twist-4 order, and will not be considered further in this paper. We focus, instead, on the role of chiral odd terms in the $g_2$ structure function up to twist 3. At this order, 
\begin{equation}
  \Xi(l,n_+) = \Lambda A_1(l^2)\,\id + A_2(l^2)\,\lslash 
    + O(\Lambda^2/Q^2)
\label{e:jetexpansion-tw3}
\end{equation} 
is nothing else than the cut quark propagator; note however, that we consider
here the full QCD vacuum rather than the perturbative one (or, in other words, the interacting rather than the free quark fields).
The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral
representation of the cut quark propagator (see, e.g., Sec.~6.3 of
\cite{D'Hoker:2004aa} and Sec.~2.7.2 of \cite{Romao:2013aa}),
\begin{align} 
  \Xi(l) =  
  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu\,\id + J_2 (\mu^2)\,\lslash \big] \,
  \delta(l^2 -\mu^2) \ ,
\label{e:jetspectral}
\end{align}
where $\mu^2$ can be interpreted as the invariant mass of the current jet, {\it
  i.e.}, of the particles going through the cut in the top blob of
Fig.\ref{fig:handbags}(a). The $J_i$ are the spectral functions of the
quark propagator, also called ``jet functions'' in
\cite{Accardi:2008ne}, that can be interpreted as the current jet mass distributions. These satisfy
\begin{align}
  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
  \int d\mu^2 J_2(\mu^2) = 1 \ .
\label{eq:jetfnsprops}
\end{align}
From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
\begin{align}
  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
  \label{eq:jet_vs_spectral}
\end{align}

\begin{figure*}[bt]
  \centering
  (a)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram0}
  \hfill
  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2}
  \hfill
  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
  \caption{Diagrams contributing to inclusive DIS scattering up to twist-3, including a jet correlator in the top part. Note the gluon attaches to both the nucleon and jet correlators. The Hermitian conjugates of diagrams (b) and (c), i.e., with gluons attaching to the right of the cut, are not shown.
  }
  \label{fig:handbags}
\end{figure*}

When inserting the jet correlator in the handbag diagram for inclusive DIS, the integration over $dl^+$, or equivalently $dl^2/(2l^-)$, is kinematically coupled to the other integrations, and induces corrections of order $O(1/Q^2)$ whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}. In this paper, where we limit our
attention to effects of order $O(1/Q)$, we can neglect $k^-$ compared to $q^-$. As a consequence, we can extend the integration over $dl^2$ to infinity, the jet correlator decouples from the parton correlator $\Phi$, and the inclusive structure functions only depend on the integrated jet correlator 
\begin{equation} 
  \Xi(l^-,{\bm l_T}) \equiv \int \frac{dl^2}{2l^-} \, \Xi(l) 
    =  \frac{\Lambda}{2 l^-}\,\xi_1 \id
    +  \xi_2 \frac{\nslash_-}{2} 
    + \text{higher\ twists} \ .
\end{equation} 
where the terms up to twist-3 are independent of ${\bm l_T}$, and the neglected higher twist terms only contribute to $O(1/Q^2)$ to the cross section. Note that thanks to Eq.~\eqref{eq:jetfnsprops} we also obtain
\begin{align}
\xi_1 &= \int d\mu^2 \frac{\mu}{\Lambda} J_1(\mu^2) 
       \equiv \frac{\mj}{\Lambda},
&
\xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ .
\end{align} 
Here, $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
It is important to notice that $\xi_2=1$ exactly due to CPT invariance
(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined. From the analytic properties of spectral functions we know that $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2
(\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the
mass of the pion, due to color confinement effects \cite{Accardi:2008ne}. Taking into account that $J_1 < J_2$, we may therefore estimate 
\begin{align}
  \label{eq:mjet}
  \mj = O(100 \text{ MeV}) \ .
\end{align}
Although $\mj$ is in general a nonperturbative quantity, it is interesting to
notice that on the perturbative vacuum, 
\begin{align*}
  \Xi^\text{pert}(l) = (\lslash + m_q \id) \, \delta(l^2-m_q^2) + O(\alpha_s) \ ,
\end{align*}
where $\mq$ is the current quark mass; one recovers, therefore, the result of the calculation with the conventional handbag diagram.
% \begin{align}
%   \label{eq:xi2_chiral_cond}
%   \mj = \frac{\Lambda}{4} \int \Tr \big[ \Xi(l) \bm 1] 
%    = \langle 0 | \bar \psi_i(0) \psi_i(0) | 0 \rangle
% \end{align}
% % \todo{[AA] 2 issues here: (1) possible factors of 4. 
% % (2) I am neglecting the sum over quarks; we have to fix that somehow but there is a little tension between the quark level $\xi^a$ and the contribution to structure function which is summed and weighted by the electron charge.} 
% On the non-perturbative vacuum, this corresponds the contribution of a quark of flavor $q$ to the chiral condensate, and is calculable in principle in lattice QCD.
% Considering the perturbative vacuum and calculating the same to leading order in the strong coupling constant, corresponds, instead, to taking the trace of the cut bare-quark propagator to obtain 
% $\mj = \,_{\text{pert}} \langle 0
% |  \bar \psi_i(0) \psi_i(0) | 0 \rangle_{\text{pert}}  = \mq$, with $\mq$ the quark mass. One recovers, therefore, the result of the calculation with the conventional handbag diagram. 
However, we are here considering non perturbative effects
on the quark fragmentation and $\mj > \mq$. 
Therefore, differently from $J_2$, the $J_1$ function leaves an imprint on the inclusive DIS cross section even in the asymptotic $Q^2 \to \infty$ regime.

@@

Extending the analysis of \cite{Accardi:2008ne} to the calculation of twist-3
structure functions requires not only to consider the $\xi_1$ term in the jet
correlator, but also quark-gluon-quark correlators in both the proton and the
vacuum as depicted in Figs.\ref{fig:handbags}(b) and (c), respectively.

In diagram (b), the $\xi_1$ terms contribute to $O(1/Q^2)$, so that up to $O(1/Q)$ these give the same contribution as in the conventional handbag calculation. The novel element in our analysis, instead, is the jet's quark-gluon-quark correlator $\Xi_A^{\mu}(l,k)$ in diagram (c), defined as 
\begin{equation} 
\begin{split} 
  \left(\Xi_A^{\mu} \right)_{ij} &=
   \frac{1}{2}\, \sum_X \int \frac{\de \eta^+\, \de^2 \bm{\eta}_T}{(2\pi)^{3}}\;
   e^{\ii k \cdot \eta}\,
   \langle 0|\,
   {\cal U}^{n_+}_{(+\infty,\eta)}\,
   g A^{\mu}(\eta)\,
   \,\psi_i(\eta)|X\rangle
   \langle X|
             \bar{\psi}_j(0)\,
   {\cal U}^{n_+}_{(0,+\infty)}
   |0\rangle \bigg|_{\eta^-=0} .
\label{e:xi_A}
\end{split} 
\end{equation}  
This diagram and its Hermitian conjugate are not only important to account for
all contribution of order $O(1/Q)$, but also to restore gauge invariance, which is broken in diagram \ref{fig:handbags}(a) due to the different mass
of the incoming and outgoing quark lines, namely, $\mq \neq \mj$.

Rather than directly using the definition \eqref{e:xi_A}, it is convenient to
calculate the inclusive cross section as an integral of the semi-inclusive
one summed over all produced hadron flavors, then utilize the QCD equation of motions, sum over all hadron flavors, and take advantage of  
\begin{align}
  \label{eq:SIDIS_to_DIS}
  \sum_h \int d^2p_{hT}\frac{dp_h^-}{2p_h^-} \Delta^h(l,p_h) = \Xi(l) \ , 
\end{align}
where $\Delta^h$ is the quark fragmentation correlator for production of a
hadron of flavor $h$ and momentum $p_h$ \cite{Bacchetta:2006tn}. In terms of
the TMD fragmentation functions we are interested in, the sum rule \eqref{eq:SIDIS_to_DIS} reads 
\begin{align}
  \label{eq:SIDIS_to_DIS_TMDlevel1}
  \sum_h \int dz d^2p_{hT} z D_1^h(z,p_{hT}) & = \xi_2 = 1   \\
  \label{eq:SIDIS_to_DIS_TMDlevel2}
  \sum_h \int dz d^2p_{hT} E^h(z,p_{hT}) & = \xi_1 = \mj / \Lambda\ ,
\end{align}
where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function, that depends on the hadron's collinear momentum fraction $z$ and transverse
momentum $p_{hT}$, and $E^h(z,p_{hT})$ is a chiral-odd twist-3 function
defined in \cite{Bacchetta:2006tn}.

The role of the $\xi_1=M_q/\Lambda$ term in inclusive DIS can be discussed by analyzing the following terms of the semi-inclusive hadronic tensor:
\begin{align}
  \label{eq:Wsidis_ini}
  2 \Lambda  W^{\mu\nu}
    & = i \frac{2\Lambda}{Q} \hat t^{[\mu}_{\phantom \perp} 
    \epsilon_\perp^{\nu]\rho}S_{\perp\rho} 
    \sum_q e_q^2
    \bigg[ 2 \xbj g_T^q(\xbj) \sum_h \int dz d^2p_{hT} D_1^{q,h}(z,p_{hT}) 
  %\\ &
  + 2 h_1^q(\xbj) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots \ ,
\end{align}
where $g_T^q$ and $\tilde E^q$ are twist-3 TMDs originating, respectively, from the quark-quark and the quark-gluon-quark fragmentation correlators. 
For clarity, here we reintroduced the quark flavor $q$, $e_q$ being its electric charge.
The first term can be easily integrated with the help of the sum rules
\eqref{eq:SIDIS_to_DIS_TMDlevel2} and \label{eq:SIDIS_to_DIS_TMDlevel2}. To integrate the second term, however, we first need make
use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a
consequence of the QCD equations of motion \cite{Bacchetta:2006tn}, then
make use of the sum rule \eqref{eq:SIDIS_to_DIS}: 
\begin{align}
  \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) 
    = \sum_h \int dz d^2p_{hT} \Big[ E^{q,h}(z,p_{hT}) - \frac{\mq}{\Lambda} z D_1^{q,h}(z,p_{hT}) \Big]
    = \xi_1 - \frac{\mq}{\Lambda} \xi_2 = \frac{\mj - \mq}{\Lambda} \ .
\end{align}
This formula is the single most important result of this paper, and provides a
non perturbative generalization of the commonly used $\int\tilde E =0$ sum
rule introduced in \cite{Jaffe:1996zw}. Indeed, calculating the jet correlator 
on the perturbative vacuum one would obtain, as already discussed, $\mj=\mq$
and the integral would vanish.
